Monte Carlo and bootstrap for ALL parameters

### 2024-08-12 All_param.Rmd
Small modifications

  # MC_df <- data.frame(useless = rep(0, n))
  MC_df <- data.frame(matrix(numeric(0), nrow = n))
  MC_est <- data.frame()

  for (b in 1:B) { # All in one "for" loop
    # Uniform sampling over the whole territory
    xy <- data.frame(a1 = runif(n, 0, 1000), a2 = runif(n, 0, 1000))
    # Variables of interest derived from the sample
    var <- as.data.frame(t(mapply(circle_ALL_, xy$a1, xy$a2)))
    nb_var <- length(var) # number of variables of interest
    MC_df <- cbind(MC_df, xy, var)
    colnames(MC_df)[((nb_var+2)*(b-1)+2):((nb_var+2)*(b)+2-1)] <- paste0(raw_names, b)[-(11:14)]
    from_local <- function(j){sum(MC_df[(nb_var+2)*(b-1)+3+j] /p)}
    est_b <- data.frame(from_local(1), from_local(5), (from_local(5))/(from_local(1)), from_local(2), from_local(6), (from_local(6))/(from_local(2)), 
                           from_local(3), from_local(7), (from_local(7))/(from_local(3)), from_local(4), from_local(8), (from_local(8))/(from_local(4)))
    nb_est <- length(est_b) # number of estimations
    MC_est <- rbind(MC_est, est_b)
    rownames(MC_est)[b] <- paste("ech", b, sep = "")
  }
  # MC_df$useless <- NULL
  MC_est <- t(MC_est)
  row.names(MC_est) <- NULL
  var_est <- function(j){var(as.vector(MC_est[j,]))}
  MC_var <- mapply(var_est, 1:nb_est)

@@

```{r}
## BCa nonparametric
# Largely based on the code given in https://gitlab.com/scottkosty/bootstrap/-/blob/master/R/bcanon.R
# Function explained in Efron and Tibshirani (1993)
# Adapted for our particular problem
bcanon <- function(df_init,est_init,est_boot_val,p,nb_var,alpha =
                     c(.025,.975)) { 
    # df_init: initial sample
    # est_init: estimation made thanks to the initial sample
    # est_boot_val: estimations made thanks to bootstrap samples
    # p: inclusion density

@@

    colnames(df_b) <- paste0(raw_names, ".MC", b)[-(11:14)]
      # c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("nb_s.MC", b, sep = ""), paste("nb_m.MC", b, sep = ""), paste("nb_b.MC", b, sep = ""), paste("vol.MC", b, sep = ""), paste("vol_s.MC", b, sep = ""), paste("vol_m.MC", b, sep = ""), paste("vol_b.MC", b, sep = ""))
    from_local <- function(j){sum(df_b[2+j] /p)} # (nb_var+2)*(b-1)
    est_b <- data.frame(from_local(1), from_local(2), from_local(3), from_local(4), from_local(5), from_local(6), from_local(7), from_local(8), 
                        (from_local(5))/(from_local(1)), (from_local(6))/(from_local(2)), 
                        (from_local(7))/(from_local(3)), (from_local(8))/(from_local(4)))
    nb_est <- length(est_b) # number of estimations
    rownames(est_b) <- paste("ech", b, sep = "")

@@

    BOOT_var[[b]] <- mapply(var, est_boot_val)
      # list(var_nb = var(est_boot_val$est_nb), var_vol = var(est_boot_val$est_vol), var_ratio = var(est_boot_val$est_ratio))
    names(BOOT_var)[b] <- paste("Variance", b, sep = "")
    BOOT_df <- c(BOOT_df, list(data_init = df_b, data_boot = df_boot))
    names(BOOT_df)[(2*b-1):(2*b)] <- c(paste("df_MC", b, sep = ""), paste("df_boot", b, sep = ""))
    BOOT_est <- c(BOOT_est, list(est_init_b = est_b, est_boot_b = est_boot_val))
    names(BOOT_est)[(2*b-1):(2*b)] <- c(paste("est_MC", b, sep = ""), paste("est_boot", b, sep = ""))

    # Confidence intervals
    norm_CI <- data.frame(useless = rep(0, 2))
    perc_CI <- data.frame(useless = rep(0, 2))
    rev_perc_CI <- data.frame(useless = rep(0, 2))
    for (l in 1:length(est_boot_val)) { # Loop: one estimator each time
      sorted_est <- sort(est_boot_val[,l])
      lim_inf <- sorted_est[floor(B2*2.5/100)]
      lim_sup <- sorted_est[B2 - floor(B2*2.5/100)]
      perc_CI <- cbind(perc_CI, data.frame(c(lim_inf, lim_sup)))
      rev_perc_CI <- cbind(rev_perc_CI, data.frame(c(as.numeric(est_b[l])*2 - lim_sup, as.numeric(est_b[l])*2 - lim_inf)))
      norm_CI <- cbind(norm_CI, data.frame(c(as.numeric(est_b[l])-qnorm(0.975)*sqrt(var(est_boot_val[,l])), as.numeric(est_b[l])+qnorm(0.975)*sqrt(var(est_boot_val[,l])))))
    }
    norm_CI$useless <- NULL
    perc_CI$useless <- NULL
    rev_perc_CI$useless <- NULL
    test <- paste0("lim_", raw_names)[-(1:2)]
    # nam_lim <- c("lim_nb", "lim_nb_s", "lim_nb_m", "lim_nb_b", 
    #              "lim_vol", "lim_vol_s", "lim_vol_m", "lim_vol_b", 
    #              "lim_ratio", "lim_ratio_s", "lim_ratio_m", "lim_ratio_b")
    colnames(norm_CI) <- nam_lim
    colnames(perc_CI) <- nam_lim
    colnames(rev_perc_CI) <- nam_lim
    BCa_CI <- bcanon(df_b, est_b, est_boot_val, p, nb_var)
    colnames(BCa_CI) <- nam_lim
    all_CI <- list(Normal = norm_CI, Percentile = perc_CI, `Reverse percentile` = rev_perc_CI, BCa = BCa_CI)
    BOOT_CI[[b]] <- all_CI
    names(BOOT_CI)[b] <- paste("CI", b, sep = "")
  }
  return(list(`Local Variables` = BOOT_df, Estimations = BOOT_est, Variances = BOOT_var, `Confidence Intervals` = BOOT_CI))
  # Local Variables: local variables (number and volume) for each point in each sample
  # Estimations: 3 estimations (number, volume, ratio volume / number) for each sample
  # Variances: mean of the bootstrap variance for each estimator
  # Confidence Intervals: 3 different forms of 95% confidence intervals, for each total / ratio
}
```

>>>>

  MC_df <- data.frame(matrix(numeric(0), nrow = n))
  MC_est <- data.frame()

  for (b in 1:B) { # All in one "for" loop
    # Uniform sampling over the whole territory
    xy <- data.frame(a1 = runif(n, 0, 1000), a2 = runif(n, 0, 1000))
    # Variables of interest derived from the sample
    all_var <- as.data.frame(t(mapply(circle_ALL_, xy$a1, xy$a2)))
    nb_var <- length(all_var) # number of variables of interest
    MC_df <- cbind(MC_df, xy, all_var)
    colnames(MC_df)[((nb_var+2)*(b-1)+1):((nb_var+2)*(b))] <- paste0(raw_names, b)[-(11:14)]
    from_local <- function(j){sum(MC_df[(nb_var+2)*(b-1)+2+j] /p)}
    est_b <- append(as.vector(mapply(from_local, 1:8)), as.vector(mapply(function(j){(from_local(j+4))/(from_local(j))}, 1:4)))
    nb_est <- length(est_b) # number of estimations
    MC_est <- rbind(MC_est, est_b)
    rownames(MC_est)[b] <- paste("ech", b, sep = "")
  }

  var_est <- function(j){var(as.vector(MC_est[,j]))}
  MC_var <- mapply(var_est, 1:nb_est)
  MC_var <- t(as.data.frame(MC_var))
  colnames(MC_est) <- paste0("est_", raw_names)[-(1:2)]
  colnames(MC_var) <- paste0("var_", raw_names)[-(1:2)]
  row.names(MC_var) <- NULL

@@

```{r}
## Nonparametric BCa
# Largely based on the code given in https://gitlab.com/scottkosty/bootstrap/-/blob/master/R/bcanon.R
# Function explained in Efron and Tibshirani (1993)
# Adapted for our particular problem
bcanon <- function(df_init,est_init,est_boot_val,p,nb_var,alpha =
                     c(.025,.975)) { 
    # df_init: initial sample
    # est_init: estimation made thanks to the initial sample
    # est_boot_val: estimations made thanks to bootstrap samples
    # p: inclusion density

@@

    colnames(df_b) <- paste0(raw_names, ".MC", b)[-(11:14)]
    from_local <- function(j){sum(df_b[2+j] /p)} # (nb_var+2)*(b-1)
    est_b <- data.frame(from_local(1), from_local(2), from_local(3), from_local(4), from_local(5), from_local(6), from_local(7), from_local(8), 
                        (from_local(5))/(from_local(1)), (from_local(6))/(from_local(2)), 
                        (from_local(7))/(from_local(3)), (from_local(8))/(from_local(4)))
    nb_est <- length(est_b) # number of estimations
    rownames(est_b) <- paste0("ech", b)
    colnames(est_b) <- paste0("est_", b)

@@

    BOOT_var[[b]] <- mapply(var, est_boot_val)
    names(BOOT_var)[b] <- paste("Variance", b, sep = "")
    BOOT_df <- c(BOOT_df, list(data_init = df_b, data_boot = df_boot))
    names(BOOT_df)[(2*b-1):(2*b)] <- c(paste("df_MC", b, sep = ""), paste("df_boot", b, sep = ""))
    BOOT_est <- c(BOOT_est, list(est_init_b = est_b, est_boot_b = est_boot_val))
    names(BOOT_est)[(2*b-1):(2*b)] <- c(paste("est_MC", b, sep = ""), paste("est_boot", b, sep = ""))

    # Confidence intervals
    norm_CI <- data.frame(useless = rep(0, 2))
    perc_CI <- data.frame(useless = rep(0, 2))
    rev_perc_CI <- data.frame(useless = rep(0, 2))
    for (l in 1:length(est_boot_val)) { # Loop: one estimator each time
      sorted_est <- sort(est_boot_val[,l])
      lim_inf <- sorted_est[floor(B2*2.5/100)]
      lim_sup <- sorted_est[B2 - floor(B2*2.5/100)]
      perc_CI <- cbind(perc_CI, data.frame(c(lim_inf, lim_sup)))
      rev_perc_CI <- cbind(rev_perc_CI, data.frame(c(as.numeric(est_b[l])*2 - lim_sup, as.numeric(est_b[l])*2 - lim_inf)))
      norm_CI <- cbind(norm_CI, data.frame(c(as.numeric(est_b[l])-qnorm(0.975)*sqrt(var(est_boot_val[,l])), as.numeric(est_b[l])+qnorm(0.975)*sqrt(var(est_boot_val[,l])))))
    }
    norm_CI$useless <- NULL
    perc_CI$useless <- NULL
    rev_perc_CI$useless <- NULL
    nam_lim <- paste0("lim_", raw_names)[-(1:2)]
    colnames(norm_CI) <- nam_lim
    colnames(perc_CI) <- nam_lim
    colnames(rev_perc_CI) <- nam_lim
    BCa_CI <- bcanon(df_b, est_b, est_boot_val, p, nb_var)
    colnames(BCa_CI) <- nam_lim
    all_CI <- list(Normal = norm_CI, Percentile = perc_CI, `Reverse percentile` = rev_perc_CI, BCa = BCa_CI)
    BOOT_CI[[b]] <- all_CI
    names(BOOT_CI)[b] <- paste0("CI", b)
  }
  return(list(`Local Variables` = BOOT_df, Estimations = BOOT_est, Variances = BOOT_var, `Confidence Intervals` = BOOT_CI))
  # Local Variables: local variables (number and volume) for each point in each sample
  # Estimations: 3 estimations (number, volume, ratio volume / number) for each sample
  # Variances: mean of the bootstrap variance for each estimator
  # Confidence Intervals: 3 different forms of 95% confidence intervals, for each total / ratio
}
```
